%describe the tasks to be completed that will satisfy the given objective
\section{Activity}

\subsection{Research}
Research the \verb=MediaPlayer= and \verb=MediaRecorder= classes and methods. List which methods you believe will be crucial in programming the alarm system.

\subsection{Explore}
Open the \verb=AlarmSystemActivity.java= file. Explore the file. Read the comments. Note the parts of the code that you will be required to fill in. They will be labeled.

\subsection{Import}
In order to use the classes and methods from APIs, you have to import the required libraries. Import the \verb=MediaPlayer= and \verb=MediaRecorder= libraries.

\subsection{Create}
Now we will create the media class instances, set them to null, and then instantiate them in the \verb=onCreate()= method. The \verb=MediaPlayer= instance needs to be instantiated with the sound loaded to play. To do this, use the create method with \verb=this= and \verb=R.raw.caralarm1= as the two parameters.

\subsection{Sound Alarm Programming}
Now, let's program the buttons to sound the alarm. When the speaker button or sound alarm button is clicked, we want to play or stop the sound depending on if the alarm is already sounding. Research how to start the \verb=MediaPlayer= and determine if it is already playing.

\subsection{Activate Programming}
Next, we will program the activate button. This will be done in the listen method of the code. There are 4 functions in the \verb=MediaRecorder= instance that must run before it can start recording. Research how \verb=MediaRecorder= works and determine what these 4 functions are. One of the functions requires an output file. The parameter for this function is \verb=audiofile.getAbsolutePath()=. The \verb=audiofile= variable was declared earlier in the code. 

\subsection{Record}
With the \verb=MediaRecorder= (mr) ready to record, determine the functions needed to start recording and code it. Why does the prepare method have to be called before the recorder is started?

\subsection{Analyze}
Next, we will analyze the recorded audio to determine if the amplitude has reached a certain point. Which method in the \verb=MediaRecorder= class do you think would be helpful in achieving this?

In order to accomplish this, we will set up a loop that continually checks the maximum amplitude reached, and then check it against a threshold we set up.

\subsection{Summary List}
The alarm system should now be working properly. Create a list of all the methods used from the \verb=MediaPlayer= and \verb=MediaRecorder= libraries with a description of what the method does and what it accomplished in the program.