%describe the tasks to be completed that will satisfy the given objective
\section{Activity}
This section describes the tasks to be completed that will satisfy the given objectives.
\subsection{Background Information}
Inheritance can be described as compile-time mechanism in Java that enables you to extend a class (called the base class or superclass) with another class (called the derived class or subclass). In Java, inheritance is utilized for two purposes, class inheritance and interface inheritance. In this lab we will be focusing mostly on class inheritance. The idea of inheritance really is easy but powerful, When you intend to create a new class and there exits a class already that includes some of the code that you want, you can derive your new class from the existing class. In doing this, you can reuse the fields and methods of the existing class without having to write (and debug!) them yourself. 

In programming languages, polymorphism implies that some code or operations or objects act otherwise in different contexts. The dictionary definition of polymorphism means a principle in biology in which an organism or species may have many different forms or phases. This principle can also be utilized on object oriented programming and languages like the Java language. Subclasses of a class can define their own unique behaviors and yet share some of the same functionality of the parent class.

\subsection{Implementation}	
This section will guide you through the completing of the lab.
\subsubsection{Create Subclasses}
Create two different subclasses of animal class and name them Wolf and Lion. And then create two subclasses of Wolf named Coyote and Hyena and two subclasses of Lion named Cougar and Leopard.

\subsubsection{Create Abstract Methods}
Provide the implementation for abstract methods of Animal class in Wolf and Lion classes.
	
\subsubsection{Passing an Argument} 
Call the super class constructor and pass ``Context" type as its argument because the Animal (parent) class takes Context type as an argument and the Wolf and Lion class constructor also takes ``Context" type as an argument.

\subsubsection{Setting the Instance Variable} 
Set the instance variable (name) of Animal class in all of Animals subclasses.

\subsubsection{Overriding Methods} 
Override the methods of Wolf and Lion in its child classes so that it would produce different sounds when clicked on different picture choices.

\subsubsection{Use Polymorphism}
In Animal activity class, use polymorphism to initialize the Animal array.




